A Descriptive Analysis of How Psychology Journals Handle Post-Publication

### 2023-12-25 manuscript_NHB.Rmd
Updated manuscript
replaced .qmd script with .rmd version

d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique','data','processed','d_journals.csv'), show_col_types = F) # journal data 
```

>>>>

d_articles <- read_csv(here('data','processed','d_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data','processed','d_journals.csv'), show_col_types = F) # journal data 
```
